Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-07 authors.tex
authors list updated
added sn06bt color curve fig
Various changes, incorporating comments from various co-authors
added System 3.3 fig and Intro, updated authors.tex, updated mag fig and lensingtest fig
Overhauled author list to allow automatic indexing

\author{Steven~A.~Rodney\altaffilmark{1,2}}

\author{Brandon Patel}

\author{Daniel Scolnic}

\author{Ryan Foley}

\author{Alberto Molino}

\author{Marusa Bradac}

\author{Gabriel Brammer}

\author{Jose~Maria~Diego}

\author{Jens Hjorth}

\author{Austin Hoag}

\author{Mathilde Jauzac}

\author{Saurabh Jha}

\author{Patrick Kelly}

\author{Daniel Lam}

\author{Julian~Merten}

\author{Johan Richard}

\author{Keren Sharon}

\author{Louis-Gregory Strolger}

\author{Tommaso Treu}

\author{Adi Zitrin}

\altaffiltext{1}{\JHU}
\altaffiltext{1}{\Rutgers}
\altaffiltext{1}{\Chicago}
\altaffiltext{1}{\Illinois}
\altaffiltext{1}{\CSIC}
\altaffiltext{1}{\SaoPaulo}
\altaffiltext{1}{\UCDavis}
\altaffiltext{1}{\STScI}
\altaffiltext{1}{\Copenhagen}
\altaffiltext{1}{\UCDavis}
\altaffiltext{1}{\Rutgers}
\altaffiltext{1}{\Berkeley}
\altaffiltext{1}{\STScI}
\altaffiltext{1}{\WKU}
\altaffiltext{1}{\UCLA}
\altaffiltext{1}{\CalTech}
\altaffiltext{2}{Hubble fellow}

>>>>

% --------------------------------------------------
% Institutions
%   define a command for each institution's mailing address
% --------------------------------------------------
\newcommand{\HubbleFellow}{Hubble Fellow}
\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 N. Charles St., Baltimore, MD 21218, USA}
\newcommand{\elsewhere}{St. Elsewhere University.}
\newcommand{\STScI}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\newcommand{\Chicago}{Department of Physics, The University of Chicago, Chicago, IL 60637, USA}
\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411, USA}
\newcommand{\LBNL}{Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA}
\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521, USA}
\newcommand{\Andalucia}{Instituto de Astrof\'isica de Andaluc\'ia (CSIC), E-18080 Granada, Spain}
\newcommand{\Cantabria}{IFCA, Instituto de F\'isica de Cantabria (UC-CSIC), Av. de Los Castros s/n, 39005 Santander, Spain}
\newcommand{\IFCA}{\Cantabria}
\newcommand{\SaoPaulo}{Instituto de Astronomia, Geof\'isica e Ci\^encias Atmosf\'ericas, Universidade de S\~ao Paulo, Cidade Universit\'aria, 05508-090, S\~ao Paulo, Brazil}
\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101, USA}
\newcommand{\AMNH}{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th Street, New York, NY 10024, USA}
\newcommand{\NYU}{Center for Cosmology and Particle Physics, New York University, New York, NY 10003, USA}
\newcommand{\DARK}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark}
\newcommand{\Copenhagen}{\DARK}
\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721, USA}
\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064, USA}
\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556, USA}
\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel}
\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854, USA}
\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA}
\newcommand{\NOAO}{National Optical Astronomical Observatory, Tucson, AZ 85719, USA}
\newcommand{\UCSB}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
\newcommand{\SantaBarbara}{\UCSB}
\newcommand{\LCOGT}{Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Goleta, California 93117, USA}
\newcommand{\Colby}{Colby College, 4000 Mayflower Hill Dr, Waterville, ME 04901, USA}
\newcommand{\Kentucky}{University of Kentucky, Lexington, KY 40506}
\newcommand{\UCDavis}{University of California Davis, 1 Shields Avenue, Davis, CA 95616}
\newcommand{\UCLA}{University of California, Los Angeles, CA 90095}
\newcommand{\CalTech}{California Institute of Technology, 1200 East California Boulevard, Pasadena, CA 91125}
\newcommand{\Durham}{Institute for Computational Cosmology, Durham University, South Road, Durham DH1 3LE, UK}
\newcommand{\KwaZulu}{Astrophysics and Cosmology Research Unit, School of Mathematical Sciences, University of KwaZulu-Natal, Durban 4041, South Africa}
\newcommand{\HongKong}{Department of Physics, The University of Hong Kong, Pokfulam Road, Hong Kong}
\newcommand{\Oxford}{Department of Physics, University of Oxford, Clarendon Laboratory, Parks Road, Oxford, UK}
\newcommand{\CRAL}{CRAL, Observatoire de Lyon, Universit\'e Lyon 1, 9 Avenue Ch. Andr\'e, F-69561 Saint Genis Laval Cedex, France}
\newcommand{\Michigan}{Department of Astronomy, University of Michigan, 1085 S. University Avenue, Ann Arbor, MI 48109, USA}
\newcommand{\Hebrew}{The Hebrew University, The Edmond J. Safra Campus - Givat Ram, Jerusalem 9190401, Israel}
\newcommand{\IllinoisAstro}{ Astronomy Department, University of Illinois at Urbana-Champaign, 1002 W.\ Green Street, Urbana, IL 61801, USA }
\newcommand{\IllinoisPhysics}{ Department of Physics, University of Illinois at Urbana-Champaign, 1110 W.\ Green Street, Urbana, IL 61801, USA }

% --------------------------------------------------
% Author list 
%   use the \affilref and \affilreftxt commands 
%   to get an author list and footnoted institutional
%   addresses that count themselves without duplicating
% --------------------------------------------------
\newcounter{affilct}
\setcounter{affilct}{0}

% --------------------------------------------------
% \affilref{refcode}
%   Use this command inside each \altaffilmark{} instance.
%   It checks if the affiliation has already been used, and generates
%   a new affiliation reference number only if needed.
%   The user-defined refcode value will then be used by \affilreftxt
%   to set the same index number in the author list at the top and 
%   the footnoted list of institutional addresses. 
\makeatletter
\newcommand{\affilref}[1]{%
    \@ifundefined{c@#1}{%
    	\newcounter{#1}%
    	\setcounter{#1}{0}%
    }{}%
    \ifthenelse{\value{#1} > 0}{%
      \ref{#1}%
    }{%
      \refstepcounter{affilct}%
    	\label{#1}%
      \ref{#1}%
    	\addtocounter{#1}{1}%
    }%
}
\makeatother

% --------------------------------------------------
% \affilreftxt{refcode}{address} : 
%   Use this command after each author definition 
%   to generate the footnote text containing one institutional
%   address for that author. 
%   It checks if the address has already been used, and generates
%   a new affiliation footnote with text only if needed.
\makeatletter
\newcommand{\affilreftxt}[2]{%
    \@ifundefined{c@#1txt}{%
    	\newcounter{#1txt}%
    	\setcounter{#1txt}{0}%
    }{}%
    \ifthenelse{\value{#1txt} > 0}{%
    }{%
      \altaffiltext{\ref{#1}}{#2}%
    	\addtocounter{#1txt}{1}%
    }%
}
\makeatother
% --------------------------------------------------

\author{Steven~A.~Rodney\altaffilmark{\affilref{JHU},\affilref{HubbleFellow}}}
\affilreftxt{JHU}{\JHU}
\affilreftxt{HubbleFellow}{\HubbleFellow}

\author{Brandon~Patel\altaffilmark{\affilref{Rutgers}}}
\affilreftxt{Rutgers}{\Rutgers}

\author{Daniel~Scolnic\altaffilmark{\affilref{Chicago}}}
\affilreftxt{Chicago}{\Chicago}

\author{Ryan Foley\altaffilmark{\affilref{IllinoisPhysics},\affilref{IllinoisAstro}}}
\affilreftxt{IllinoisPhysics}{\IllinoisPhysics}
\affilreftxt{IllinoisAstro}{\IllinoisAstro}

\author{Alberto Molino\altaffilmark{\affilref{Andalucia},\affilref{SaoPaulo}}}
\affilreftxt{Andalucia}{\Andalucia}
\affilreftxt{SaoPaulo}{\SaoPaulo}

\author{Mathilde Jauzac\altaffilmark{\affilref{Durham},\affilref{KwaZulu}}}
\affilreftxt{Durham}{\Durham}
\affilreftxt{KwaZulu}{\KwaZulu}

\author{Gabriel Brammer\altaffilmark{\affilref{STScI}}}
\affilreftxt{STScI}{\STScI}

\author{Marusa Bradac\altaffilmark{\affilref{UCDavis}}}
\affilreftxt{UCDavis}{\UCDavis}

\author{Jose~Maria~Diego\altaffilmark{\affilref{Cantabria}}}
\affilreftxt{Cantabria}{\Cantabria}

\author{Jens Hjorth\altaffilmark{\affilref{DARK}}}
\affilreftxt{DARK}{\DARK}

\author{Or Graur\altaffilmark{\affilref{NYU},\affilref{AMNH}}}
\affilreftxt{NYU}{\NYU}
\affilreftxt{AMNH}{\AMNH}

\author{Austin Hoag\altaffilmark{\affilref{UCDavis}}}
\affilreftxt{UCDavis}{\UCDavis}

\author{Saurabh Jha\altaffilmark{\affilref{Rutgers}}}
\affilreftxt{Rutgers}{\Rutgers}

\author{Patrick Kelly\altaffilmark{\affilref{Berkeley}}}
\affilreftxt{Berkeley}{\Berkeley}

\author{Daniel Lam\altaffilmark{\affilref{HongKong}}}
\affilreftxt{HongKong}{\HongKong}

\author{Elinor Medezinski\altaffilmark{\affilref{JHU},\affilref{Hebrew}}}
\affilreftxt{JHU}{\JHU}
\affilreftxt{Hebrew}{\Hebrew}

\author{Julian~Merten\altaffilmark{\affilref{Oxford}}}
\affilreftxt{Oxford}{\Oxford}

\author{Johan Richard\altaffilmark{\affilref{CRAL}}}
\affilreftxt{CRAL}{\CRAL}

\author{Keren Sharon\altaffilmark{\affilref{Michigan}}}
\affilreftxt{Michigan}{\Michigan}

\author{Louis-Gregory Strolger\altaffilmark{\affilref{STScI},\affilref{WKU}}}
\affilreftxt{STScI}{\STScI}
\affilreftxt{WKU}{\WKU}

\author{Tommaso Treu\altaffilmark{\affilref{UCLA}}}
\affilreftxt{UCLA}{\UCLA}

\author{Liliya Williams\altaffilmark{\affilref{Minnesota}}}
\affilreftxt{Minnesota}{\Minnesota}

\author{Adi Zitrin\altaffilmark{\affilref{CalTech},\affilref{HubbleFellow}}}
\affilreftxt{CalTech}{\CalTech}

### 2015-04-07 preamble.tex
incorporated most comments from JH,KS, others
added System 3.3 fig and Intro, updated authors.tex, updated mag fig and lensingtest fig
Overhauled author list to allow automatic indexing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% changetext  mode settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchangetext
  % Changed text is highlighted in bold, blue font 
  \newcommand{\change}[1]{{\bf \textcolor{blue}{#1}}}
\else
  % Changed text is indistinguishable
  \newcommand{\change}[1]{#1}
\fi

%%%%%%%%%%%%%%%%%%%%
% PACKAGES INCLUDED
%%%%%%%%%%%%%%%%%%%%
\usepackage{natbib}   % reference citations and bibliography
\usepackage{amsmath}  % extended math symbols
\usepackage{verbatim} % verbatim text formatting
\usepackage{enumerate}% enumerated lists
\usepackage{amssymb}  % extended symbols lib
%\usepackage{url}      % url text formatting
\usepackage{hyperref}      % url text formatting
\usepackage[usenames]{color}  % colored text
%\usepackage{multirow}  % muti-row table cells
%\usepackage{amsmath}  % extended equations lib (split)
%\usepackage{mathrsfs} % extended math fonts (mathscr)
%\usepackage{paralist} % inline enumeration (for Table ref lists)
%\usepackage{authblk}
\usepackage{appendix}

@@

% Missions:
\def\Hubble{{\it Hubble}}
\def\Hubbles{{\it Hubble's}}
\def\Spitzer{{\it Spitzer}}
\def\Chandra{{\it Chandra}}
\def\Herschel{{\it Herschel}}
\def\XMM{{\it XMM}}

% Institutions
\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, Baltimore, MD 21218.}
\newcommand{\elsewhere}{St. Elsewhere University.}
\newcommand{\STScI}{Space Telescope Science Institute, Baltimore, MD 21218.}
\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411.}
\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521.}
\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101.}
\newcommand{\Copenhagen}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark.}
\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721.}
\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064.}
\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556.}
\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel.}
\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854.}
\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138.}
\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA.}

>>>>

%%%%%%%%%%%%%%%%%%%%
% PACKAGES INCLUDED
%%%%%%%%%%%%%%%%%%%%
\usepackage{ifthen}
\usepackage{natbib}   % reference citations and bibliography
\usepackage{amsmath}  % extended math symbols
\usepackage{verbatim} % verbatim text formatting
\usepackage{enumerate}% enumerated lists
\usepackage{amssymb}  % extended symbols lib
%\usepackage{url}      % url text formatting
\usepackage{hyperref}      % url text formatting
\usepackage[usenames,dvipsnames]{xcolor}  % colored text
%\usepackage{multirow}  % muti-row table cells
%\usepackage{amsmath}  % extended equations lib (split)
%\usepackage{mathrsfs} % extended math fonts (mathscr)
%\usepackage{paralist} % inline enumeration (for Table ref lists)
%\usepackage{authblk}
\usepackage{appendix}
%\usepackage{array}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% changetext  mode settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchangetext
  % Changed text is highlighted in bold, blue font 
  \newcommand{\change}[1]{{\bf \textcolor{blue}{#1}}}
  \newcommand{\changeB}[1]{{\bf \textcolor{blue}{#1}}}
  \newcommand{\changeG}[1]{{\bf \textcolor{ForestGreen}{#1}}}
  \newcommand{\changeR}[1]{{\bf \textcolor{red}{#1}}}
\else
  % Changed text is indistinguishable
  \newcommand{\change}[1]{#1}
  \newcommand{\changeB}[1]{#1}
  \newcommand{\changeG}[1]{#1}
  \newcommand{\changeR}[1]{#1}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New table column types, allowing left- or right-justified text in 
% paragraph mode, that also allows manual line-breaks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

% Missions:
\def\HST{{\it HST}}
\def\Hubble{{\it Hubble}}
\def\Hubbles{{\it Hubble's}}
\def\Spitzer{{\it Spitzer}}
\def\Chandra{{\it Chandra}}
\def\Herschel{{\it Herschel}}
\def\XMM{{\it XMM}}
